Efficient Non-incremental Constructive Solid Geometry Evaluation for Triangular Meshes

### 2016-05-09 paper.tex
change to work office

\usepackage{color}

@@

\IEEEtitleabstractindextext{
\begin{abstract}
\end{abstract}

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM). It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference. CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations.
\newline

{\color{red}{
Main Contribution:

1. We develop a united representation of intersection lines between CSG primitives. Under this representation, Face re-tessellation and classification can be done robustly in any degenerate cases by our pipeline, while keeping good performance.

2. Unlike any of the previous method, during the algorithm, we conduct point-in-polyhedron tests only on single seed vertex. We develop a propagating to spread the classification information from the seed vertex into the whole CSG. In addition, because of this, we do not need to build a full space division to accelerate point-in-polyhedron tests, which is usually time-consuming.
}}

@@

\subsection{United Representation of Intersection Construction}
\label{sec:overview:isect}

\subsection{Multilevel Flood-filling Classification}

\section{United Representation of Primitive Intersection}
{\color{red}{
Primitive intersects primitive, generating intersection line segments (Fig. \ref{fig_raw1}).

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{raw1}\\
  \caption{triangle contains intersection lines, two-primitive case}\label{fig_raw1}
\end{figure}

Considering degenerate cases in n-primitives CSG can be very complex (Fig. \ref{fig_raw2}).

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{raw2}\\
  \caption{triangle contains intersection lines, n-primitives degenerate cases}\label{fig_raw2}
\end{figure}

We converted it into a united representation, making it clear and easy to process by the following process (Fig. \ref{fig_raw3}).

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{raw3}\\
  \caption{triangle contains intersection lines, n-primitives degenerate cases, using united representation}\label{fig_raw3}
\end{figure}
}}

\subsection{Plane-based Triangle Intersection}

{\color{red}{why using triangle intersection, rather than edge-face based, etc. --- for coplanar test.}}
\newline\newline

@@

\subsection{Generating United Representation}

{\color{red}{Mainly deal with intersection between intersection line segments.}}

\section{Multi-level Flood-filling Classification}
\label{section:floodfill}

{\color{red}{Flood-filling is all about giving a seed and propagation. In this chapter, from down to top, we introduce this process and explain how it can save computation time.}}

>>>>

@@

\IEEEtitleabstractindextext{
\begin{abstract}
  In this paper, we propose an efficient non-incremental approach to evaluate the boundary of constructive solid geometry (CSG). The face membership classification step is a bottleneck in many existing CSG evaluation approaches. The key idea of our approach is to use local coherence of space labels to accelerate this step. We employ a two-level grouping scheme to group faces that share the same space labels. Therefore, these common space labels can be shared within each group to avoid repetitive computation. Our method is optimized for a non-incremental evaluation. It generates the entire result model at once, rather than performing a step-by-step evaluation of Boolean operations. To achieve a robust evaluation, our approach introduces plane-based geometry into the intersection computation step. Comparison experiments with state-of-the-art techniques show that our method can more efficiently perform boundary evaluation of both trivial and complicated CSG with massive faces while maintaining robustness.
\end{abstract}

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM). It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference. CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations..

CSG can be converted into the widely-used  boundary representation (i.e., triangle mesh) through boundary evaluation. Most boundary evaluation methods are based first on intersection computation and then on face membership classification. Robustness and efficiency are their major issues. During the last three decades, many techniques have been developed to solve these problems. However, the efficiency of face membership classification still needs improvement.

Computing face space labels is the basis of face classification with respect to CSG. For each face, the number of space labels to be computed is equal to the number of primitives. For large CSG with massive faces and primitives, computing these space labels can be very time-intensive. A common acceleration method is to use localized schemes. This method is based on the local coherence of space labels: if a face is inside (or outside) a specific primitive, the face's neighborhoods are likewise often inside (or outside) the primitive. Determining whether two adjacent faces share the same space labels is relatively simple (see also Section \ref{sec:framework}); therefore, we can locally group together faces of the same labels and reuse space labels to save computation.

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{cluster}\\
  \caption{2D illustration of grouping schemes. The boundaries of polygons are edges. Suppose each input mesh consists of hundreds of edges (not shown in the figure). Edges are grouped using (a) voxels, (b) octree cells, and (c) edges as the grouping units. Different groups in (c) are marked by different colors.} \label{fig:cluster}
\end{figure}

Several recent studies \cite{campen2010exact, pavic2010hybrid, wang2011approximate} have used such localized schemes. These approaches often use the cube (e.g., voxels, octree cells) as the basic grouping unit to reuse the space division data structures constructed during the intersection computation. However, using the cube as a basic grouping unit has several disadvantages. In general, connected faces with the same space labels should be grouped together. Thus, an ideal face group is a union of connected faces and can be of any shape. The cube-based grouping scheme can only provide a rough approximation of that shape. Therefore, extra computation, which is usually time-consuming, is needed to classify those ungrouped faces. For example, in Figs. \ref{fig:cluster}(a) and (b), the red cubes contain the intersection of two primitives. Thus, the edges (faces in 3D) in these red cubes should belong to different groups (because they have different labels). However, the size of cubes cannot be illimitably small to distinguish these different groups. Therefore, these edges in the red cubes are left as ungrouped edges. In contrast, a face-based grouping scheme can easily handle groups of arbitrary shapes and is potentially more efficient for face classification (Fig. \ref{fig:cluster}(c)).

Another limitation of prior exact evaluation algorithms is that most of them are incremental ones \cite{campen2010exact, feito2013fast, bernstein2009fast}. This means that they can evaluate only one Boolean operation at a time. For a large CSG tree with more than two primitives, incremental algorithms have to decompose the CSG into a series of Boolean operations and then incrementally evaluate each one. This strategy is highly inefficient because it unnecessarily computes the CSG intermediate results. Incremental algorithms have been more popular for a considerable time because human designers typically construct CSG models by progressively adding primitives. However, recent techniques---such as GPU-based approximate evaluation algorithms \cite{pavic2010hybrid, wang2011approximate} and CSG visualization algorithms \cite{hable2007cst, rossignac2011ordered}---are more suitable for such a preview computation. Therefore, exact evaluation algorithms are now more likely to be used for final mesh generation (after all the primitives are added), where a non-incremental algorithm has more advantages.

In this paper, we propose a method to perform CSG boundary evaluation with triangular mesh primitives. The proposed method uses the face (i.e., a triangle in our implementation) as the basic unit of the grouping and applies a flood-filling algorithm to group faces. Our method utilizes the local coherence of space labels. It propagates face space labels between adjacent faces and adjacent groups to save computation of space labels. The most prominent characteristics of our method are outlined below.
\vspace{0.0em}
\begin{itemize}[leftmargin=*]
  \item{\textbf{Face classification using two-level grouping}}~~~~To efficiently classify faces, we use a two-level grouping scheme to reuse space labels. Input faces are firstly grouped into first-level groups at the primitive level; then, the first-level groups are further divided into second-level groups according to their labels (Fig. \ref{fig_overview}(d)). A flood-filling algorithm is applied to enable efficient grouping and label sharing among adjacent faces. This framework makes a balance between the benefit of face label sharing and the cost of grouping faces for the best performance.

  \vspace{0.5em}
  \item{\textbf{Efficient non-incremental evaluation}}~~~~Unlike many existing Boolean methods \cite{granados2003boolean, bernstein2009fast, campen2010exact, feito2013fast}, the proposed method can perform non-incremental evaluation of CSG, which computes the entire final model directly. Our approach is more efficient at evaluating large CSGs because it computes no intermediate results in the internal nodes of CSG trees. A non-incremental evaluation is more difficult to perform because the conditions of the intersection and face classification are more complicated. We developed a set of techniques, including face-nested binary space partitioning (BSP) and multi-level CSG trimming, to make our method highly efficient for non-incremental evaluation.

  \vspace{0.5em}
  \item{\textbf{Robustness and exactness}}~~~~In the field of solid modeling, efficiency without robustness is impractical. We therefore adopt a series of schemes to make our method robust. To avoid the introduction of errors during intersection computation, we combine a triangle-triangle intersection algorithm \cite{moller1997fast} with a plane-based representation \cite{sugihara1990solid}. In addition, an exact BSP construction technique \cite{bernstein2009fast, campen2010exact} is adopted to enhance the robustness of face classification.
\end{itemize}
\vspace{0.5em}

Experiments performed confirm that our method is more efficient than state-of-the-art techniques \cite{cgal:hk-bonp3-15a, campen2010exact, feito2013fast, Maya2015}. It can quickly and robustly perform CSG evaluations not only for trivial CSGs, such as one with single Boolean operation, but also for large CSGs with hundreds of primitives.

@@

\subsection{Plane-based Intersection Computation}
\label{sec:overview:isect}

In this step, we compute all intersections between primitives and record them in intersected faces (e.g., the red triangles in Fig. \ref{fig_overview}(c)) for further computation. Because we have already constructed the octree and obtained its cell classification, it is instantly known that intersection between faces occurs only within critical cells. Thus, we limit the intersection test within these critical cells. The intersection test is performed for every pair of faces in each critical cell. We assume that primitives are not self-intersected; therefore, tests for faces from the same primitives are unnecessary.

The triangle-triangle intersection test always incurs robustness issues. To avoid an unexpected failure caused by numeric errors, we integrate a plane-based representation of polyhedra \cite{sugihara1990solid} into the triangle-triangle intersection test. Adaptive precision predicate technique \cite{shewchuk1997adaptive} is applied for efficiency of plane-based geometry computation. Details are provided in Section \ref{section:isect}.

\subsection{Face Classification Using Two-level Grouping}

Face classification using two-level grouping is the most novel step of our algorithm. For each primitive face, we must determine whether it, or its part (when the face intersects with other faces), belongs to the final model. A breadth-first flood-filling algorithm is used to traverse faces of each primitive. Starting from a random seed whose space labels are all computed, these labels propagate to neighboring faces and vary according to intersection conditions (Fig. \ref{fig_overview}(d)). Each face is instantly classified once all of its space labels are computed. We use a two-level face grouping scheme to enable the maximum information reuse. The first level is the \emph{inter-primitive} level; the second is the \emph{intra-primitive} level. When visiting an intersected face, constrained Delaunay triangulation \cite{chew1989constrained} is applied to subdivide the face into smaller triangles, followed by individual classification of the subdivided triangles using BSP techniques. The robustness of this step is ensured by the exact BSP computation technique \cite{bernstein2009fast}. Details are shown in Section \ref{section:floodfill}.

\section{Plane-based Intersection Computation}

\label{section:isect}

In this step, intersections between faces are computed through the triangle-triangle intersection test within each critical cell. We adopt M\"{o}ller's intersection detection algorithm \cite{moller1997fast} for this test on account of the algorithm's efficiency and simplicity. However, because collision detection algorithms are often accompanied by non-robustness problems, a conventional implementation of the algorithm may cause unpredictable results. Therefore, we integrate plane-based geometry representation \cite{sugihara1990solid} into M\"{o}ller's algorithm to make it unconditionally precise and robust.

\subsection{Intersection Detection}

@@

\subsection{Intersection Recording}
\label{sec:isecthandle}

The information of intersection is stored in the intersected faces where the intersection occurs. Because the intersection is generated by two (or more) faces, both (all) faces are intersected faces and store the same copy of intersection information.

Each intersected face maintains two important lists for further processing: \emph{cross list} and \emph{coplanar list}. The cross list stores the end points of intersections, the associated faces of the intersections, and the primitives to which these associated faces belong. The coplanar list is relatively simple. It only stores coplanar faces and the primitives to which these coplanar faces belong.

Moreover, in order to reconstruct geometry connectivity and to avoid coincident vertices in the final model, coincident points detected during intersection computation are merged. A \emph{point list} for each intersected face $F$ is used for this purpose. The list stores all the points inside $F$ or on the boundary of $F$. When introducing new vertices into the face (e.g., recording the new intersection line into the cross list, the two end points of the intersection line segment are newly introduced vertices), we determine if there exists a coincident point in the point list. Coincident points are merged. In addition, because the points on the edges of $F$ are shared by adjacent faces, these points should be added to the corresponding point lists of both two adjacent faces.

There is a degenerate condition for intersection recording: $F_1$ and $F_2$ may intersect on a single point. We treat this condition as $F_1$ and $F_2$ being non-intersecting but add the intersected point into the point lists of both faces. Another point to notice is that if $F_1$ and $F_2$ are coplanar and overlap, $F_1$ is added to the coplanar list of $F_2$ and vice versa. No new point is introduced under this condition.

\section{Face Classification}
\label{section:floodfill}
